---
title: "Final term Project - MLD"
author: "___________"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 8.5) # fig.width = 7.25

# Course: ECON 5300
# Title: Final Term Project - MLD
# Purpose: conclude mortgage lending institutions discrimination against minorities
# Author: ________________

```

# Goal of the EDA:

The goal of this EDA is to understand what is the effect of minorities and racial/ethenic groups on mortgage lending , and to coclude the finding.

# Prerequisites for analysis

Following needs to be prior to any analysis:

+ Clear your environment
+ Load required packages
+ Organize your work and point to the right directories

```{r include=FALSE}

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environment of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE) {
  lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
         detach, character.only = TRUE, unload = TRUE)
}

# load required libraries
library(tidyverse)
library(here)
library(skimr)
library(janitor)
library(gridExtra)
library(GGally)
library(knitr)
library(kableExtra)
library(pander)
library(formattable)
library(ggrepel)
library(scales)
library(psych)

```

Following needs to be done prior to starting an EDA:

+ Load raw data
+ Make changes to data based on business rules definitions
+ Perform joins as required

```{r include=FALSE}

raw_data <- read_csv("./MLD Data File-1.csv")

```

```{r}
mld_data <- raw_data %>% 
  rename(cred_meet = GDLIN, other_oblg = OBRAT) %>%
  filter(cred_meet != 666, MALE != ".", MARRIED !=".")
              mutate( MARRIED = factor(MARRIED),
                      cred_meet = factor(cred_meet),
                      BLACK = factor(BLACK),
                      HISPAN = factor(HISPAN),
                      MALE = factor(MALE),
                      APPROVE = factor(APPROVE))

str(mld_data)
```

# Summary of data

We look at a summary of data:

+ to know how clean the data is
+ to check if typical values (in the middle or at extremes) make sense 
+ to confirm if there missing values that need to be addressed

The **skim** function in the **skimr** package summarises columns separately by data type - (here) factor variables followed by integers and numerics

```{r, results = 'asis'}

panderOptions('table.split.table', Inf)
skim(mld_data) %>% pander()

```

**Conclusions**:

+ There are 1989 records with no missing values
+ Majority of loans are approved
+ Most people are not black
+ Mostly people credit conditions are met
+ Almost all loan applicants are non-hispanic 
+ Male applicants are male
+ Majority of people applying for loan are married

+ We have false data in dataset:
  - Credit meet has a value (666) for 2 records
  - Male and married have 15 and 3 observations with value (.)

# Exploratory Data Analysis (Basic)

## Univariate non-graphical -- Categorical
=========================================
```{r}
# Inspect descriptive statistics of data
summary(mld_data)

```

**Conclusions:**

+ Other obligation has min - 0.0 and maximum percentage value as - 95%
+ Loan Approval price has min amount - 0.02105 and maximum amount is - 2.57143. What is the unit here?


```{r}
# number of observations also proportion for Approval status
tabyl(mld_data$APPROVE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Approve", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


```{r}
# number of observations also proportion for Black applicant
tabyl(mld_data$BLACK) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Black Applicants", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


```{r}
# number of observations also proportion for Black applicant
tabyl(mld_data$cred_meet) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Credit Cond Met", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


```{r}
# number of observations also proportion for Black applicant
tabyl(mld_data$HISPAN) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Hispanic Applicants", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


```{r}
# number of observations also proportion for Black applicant
tabyl(mld_data$MALE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Male Applicants", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


```{r}
# number of observations also proportion for Black applicant
tabyl(mld_data$MARRIED) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Married Applicants", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```


## Univariate graphical -- Categorical
=========================================

We need to look at frequencies of categorical variables to confirm the distribution

```{r}
# Code histograms using grid.arrange so can see all quant variables together
# Graph between each promo and its count
# Graph between each flavor and its count
# graph between each brand, its falor and count
# and vice versa
grid.arrange(
  mld_data %>% 
    ggplot(aes(BLACK, fill = cred_meet)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(HISPAN, fill = cred_meet)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(MALE, fill = cred_meet)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(MARRIED, fill = cred_meet)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  ncol = 2
)


# Graph between each promo and its count
# Graph between each adv and its count
# graph between each promo with adv
# and vice versa
grid.arrange(
  mld_data %>% 
    ggplot(aes(BLACK, fill = APPROVE)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(HISPAN, fill = APPROVE)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(MALE, fill = APPROVE)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(MARRIED, fill = APPROVE)) +
      geom_bar(position = "dodge") +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  ncol = 2
)

```


**Univariate non-graphical -- Quantitative**
=========================================

```{r}
# Get descrptive stats 
summary(mld_data)

```

## Univariate graphical -- Quantitative
=========================================

We need to look at histograms of quantitative variables to confirm what we have just seen. 

```{r message = FALSE}
# Code histograms using grid.arrange so can see all quant variables together
# histogram to see how sales, price, unit and volume is distributed in sample given
grid.arrange(
  mld_data %>% 
    ggplot(aes(other_oblg)) +
      geom_histogram() +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  mld_data %>% 
    ggplot(aes(LOANPRC)) +
      geom_histogram() +
       theme_minimal() +
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "#D3D3D3")),
  ncol = 2
)
```

**Boxplots of quantitative data**

```{r}
# Set grid pattern for graph arrangement
# draw the box plots to see the variation in all quantitative variables : unit, price,volume, sales
par(mfrow = c(1, 2))
boxplot(mld_data$other_oblg, main = "Other Obligations")
boxplot(mld_data$LOANPRC, main = "Loan Amount")
```


Multivariate non-graphical -- Categorical
=========================================
Use cross-tabs for counts/proportion/percent 

```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(MARRIED, cred_meet) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(BLACK, cred_meet) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(HISPAN, cred_meet) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(MALE, cred_meet) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(MARRIED, APPROVE) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(BLACK, APPROVE) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(HISPAN, APPROVE) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```


```{r}

# Proportions might be more informative
mld_data %>% 
  tabyl(MALE, APPROVE) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>%  
  adorn_pct_formatting(digits = 0) %>% 
  kableExtra::kable() %>% 
  kable_styling(full_width = FALSE)

```

## Multivariate non-graphical -- Quantitative
=========================================

The standard measure we can use to assess relationships is correlation.

```{r}
# Find correlation of quantiative variables

cor(mld_data[, c(3,8)])

```

Multivariate graphical code -- Quantitative
=========================================

```{r message=FALSE}

# the correlation plot from the psych package -- `install.package("psych")` if not installed already

pairs.panels(mld_data[, c(3,8)])

```

