---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  word_document: default
always_allow_html: yes
---


```{r echo = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environment of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE) {
  lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
         detach, character.only = TRUE, unload = TRUE)}

```

```{r echo = FALSE}
library(tidyverse)
library(ggplot2)
library(Rcpp)
library(kableExtra)
library(aod)
library(janitor)
library(summarytools)
library(xtable)
library(pastecs)
library(magrittr)
library(qwraps2)
library(stargazer)
library(stats)
```

```{r echo = FALSE}
raw_data <- read_csv("./MLD Data File-1.csv")

summary(raw_data)
```

```{r}
mld <- raw_data %>%
          filter(GDLIN != 666, MARRIED !=".") %>%
          mutate( MARRIED = factor(MARRIED),
                      GDLIN = factor(GDLIN),
                      BLACK = factor(BLACK),
                      HISPAN = factor(HISPAN),
                      APPROVE = factor(APPROVE))

summary(mld)


```



Descriptive statistic
```{r}
mld_black <- mld %>% filter(BLACK == 1) %>%
                    select(-BLACK,-HISPAN)
mld_hispan <- mld %>% filter(HISPAN == 1) %>%
                      select(-BLACK,-HISPAN)
mld_white <- mld  %>% filter(HISPAN == 0 & BLACK == 0) %>%
                        select(-BLACK,-HISPAN)
```

#Overall Descriptive Statistic
###Approve
```{r}
mld %>%
  tabyl(APPROVE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Approve", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)

```

###Married
```{r}
mld %>%
  tabyl(MARRIED) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Married", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

###GLIND
```{r}
mld %>%
  tabyl(GDLIN) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Guideline", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

###Black
```{r}
mld %>%
  tabyl(BLACK) %>%
  adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Black", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```
### Hispan
```{r}
mld %>%
  tabyl(HISPAN) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Hispan", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```


### Male
```{r}
mld %>%
  tabyl(MALE) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Male", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Other obligation
```{r}
desc_tab<-rbind(c(min(mld$OBRAT), mean(mld$OBRAT), max(mld$OBRAT), median(mld$OBRAT), sd(mld$OBRAT)),
      c(min(mld$LOANPRC), mean(mld$LOANPRC), max(mld$LOANPRC), median(mld$LOANPRC), sd(mld$LOANPRC))) 
row.names(desc_tab) <- c("Other Obligation", "Loan amount/purchase") 

desc_tab %>% round(2) %>%
      kableExtra::kable(col.names = c("Min", "Mean", "Max", "Median", "Standard Deviation")) %>% 
      kable_styling(full_width = FALSE)
```

# Black subset Descriptive Statistic
### Approve
```{r}
mld_black %>%
  tabyl(APPROVE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Approve", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)



```

### Married
```{r}
mld_black %>%
  tabyl(MARRIED) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Married", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### GLIND
```{r}
mld_black %>%
  tabyl(GDLIN) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Guideline", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Male
```{r}
mld_black %>%
  tabyl(MALE) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Male", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Other obligation
```{r}
desc_tab<-rbind(c(min(mld_black$OBRAT), mean(mld_black$OBRAT), max(mld_black$OBRAT),median(mld_black$OBRAT), sd(mld_black$OBRAT)),
      c(min(mld_black$LOANPRC), mean(mld_black$LOANPRC), max(mld_black$LOANPRC), median(mld_black$LOANPRC), sd(mld_black$LOANPRC))) 
row.names(desc_tab) <- c("Other Obligation", "Loan amount/purchase") 

desc_tab %>% round(2) %>%
      kableExtra::kable(col.names = c("Min", "Mean", "Max", "Median","Standard Deviation")) %>% 
      kable_styling(full_width = FALSE)
```


# Hispan subset Descriptive Statistic
### Approve
```{r}
mld_hispan %>%
  tabyl(APPROVE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Approve", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)



```

### Married
```{r}
mld_hispan %>%
  tabyl(MARRIED) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Married", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### GLIND
```{r}
mld_hispan %>%
  tabyl(GDLIN) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Guideline", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Male
```{r}
mld_hispan %>%
  tabyl(MALE) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Male", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Other obligation
```{r}
desc_tab<-rbind(c(min(mld_hispan$OBRAT), mean(mld_hispan$OBRAT), max(mld_hispan$OBRAT), median(mld_hispan$OBRAT), sd(mld_hispan$OBRAT)),
      c(min(mld_hispan$LOANPRC), mean(mld_hispan$LOANPRC), max(mld_hispan$LOANPRC), median(mld_hispan$LOANPRC),sd(mld_hispan$LOANPRC))) 
row.names(desc_tab) <- c("Other Obligation", "Loan amount/purchase") 

desc_tab %>% round(2) %>%
      kableExtra::kable(col.names = c("Min", "Mean", "Max", "Median","Standard Deviation")) %>% 
      kable_styling(full_width = FALSE)
```

# White subset Descriptive Statistic
### Approve
```{r}
mld_white %>%
  tabyl(APPROVE) %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Approve", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)



```

### Married
```{r}
mld_white %>%
  tabyl(MARRIED) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Married", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### GLIND
```{r}
mld_white %>%
  tabyl(GDLIN) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Guideline", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Male
```{r}
mld_white %>%
  tabyl(MALE) %>%
   adorn_totals(where = c("row"))  %>%
  adorn_pct_formatting() %>% 
  kableExtra::kable(col.names = c("Male", "Count", "Percent")) %>% 
  kable_styling(full_width = FALSE)
```

### Other obligation
```{r}
desc_tab<-rbind(c(min(mld_white$OBRAT), mean(mld_white$OBRAT), max(mld_white$OBRAT), median(mld_white$OBRAT),sd(mld_white$OBRAT)),
      c(min(mld_white$LOANPRC), mean(mld_white$LOANPRC), max(mld_white$LOANPRC), median(mld_white$LOANPRC),sd(mld_white$LOANPRC))) 
row.names(desc_tab) <- c("Other Obligation", "Loan amount/purchase") 

desc_tab %>% round(2) %>%
      kableExtra::kable(col.names = c("Min", "Mean", "Max", "Median","Standard Deviation")) %>% 
      kable_styling(full_width = FALSE)
```



# Estimate Logit Model
```{r}
mld <- mld %>%
        select(-MALE)

LogitOverallModel <- glm(APPROVE ~ ., data = mld, 
                 family = "binomial")
summary(LogitOverallModel)
```

```{r}
#Generate Odds Ratios
exp(coef(LogitOverallModel))

logLik(LogitOverallModel)
```

```{r}
meanOBRAT <- mean(mld$OBRAT)
meanLNPRC <- mean(mld$LOANPRC)

#Define prototypical loan applicants (you will need more than 3)
#White - married - guideline
prototype1 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT = meanOBRAT, BLACK = "0", HISPAN = "0", LOANPRC = meanLNPRC)
#White - married - no guideline
prototype2 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT = meanOBRAT, BLACK = "0", HISPAN = "0", LOANPRC = meanLNPRC)
#White - singel - guideline
prototype3 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT = meanOBRAT, BLACK = "0", HISPAN = "0", LOANPRC = meanLNPRC)
#White - single - no guideline
prototype4 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT = meanOBRAT, BLACK = "0", HISPAN = "0", LOANPRC = meanLNPRC)

#Black - married - guideline
prototype5 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT= meanOBRAT, BLACK = "1", HISPAN = "0", LOANPRC = meanLNPRC)
#Black - married - no guideline
prototype6 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT=meanOBRAT, BLACK = "1", HISPAN = "0", LOANPRC = meanLNPRC)
#Black - singel - guideline
prototype7 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT=meanOBRAT, BLACK = "1", HISPAN = "0", LOANPRC = meanLNPRC)
#Black - single - no guideline
prototype8 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT=meanOBRAT, BLACK = "1", HISPAN = "0", LOANPRC = meanLNPRC)


#hispan - married - guideline
prototype9 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT=meanOBRAT, BLACK = "0", HISPAN = "1", LOANPRC = meanLNPRC)
#hispan - married - no guideline
prototype10 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT=meanOBRAT, BLACK = "0", HISPAN = "1", LOANPRC = meanLNPRC)
#hispan - singel - guideline
prototype11 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT=meanOBRAT, BLACK = "0", HISPAN = "1", LOANPRC = meanLNPRC)
#hispan - single - no guideline
prototype12 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT=meanOBRAT, BLACK = "0", HISPAN = "1", LOANPRC = meanLNPRC)


```

```{r}

prototype1$logitprob <- predict(LogitOverallModel, newdata = prototype1, type ="response")
prototype1

prototype2$logitprob <- predict(LogitOverallModel, newdata = prototype2, type ="response")
prototype2

prototype3$logitprob <- predict(LogitOverallModel, newdata = prototype3, type ="response")
prototype3

prototype4$logitprob <- predict(LogitOverallModel, newdata = prototype4, type ="response")
prototype4

prototype5$logitprob <- predict(LogitOverallModel, newdata = prototype5, type ="response")
prototype5

prototype6$logitprob <- predict(LogitOverallModel, newdata = prototype6, type ="response")
prototype6

prototype7$logitprob <- predict(LogitOverallModel, newdata = prototype7, type ="response")
prototype7

prototype8$logitprob <- predict(LogitOverallModel, newdata = prototype8, type ="response")
prototype8

prototype9$logitprob <- predict(LogitOverallModel, newdata = prototype9, type ="response")
prototype9

prototype10$logitprob <- predict(LogitOverallModel, newdata = prototype10, type ="response")
prototype10

prototype11$logitprob <- predict(LogitOverallModel, newdata = prototype11, type ="response")
prototype11

prototype12$logitprob <- predict(LogitOverallModel, newdata = prototype12, type ="response")
prototype12

```

```{r}
logitestimate <- rbind(prototype1,
                          prototype2,
                          prototype3,
                          prototype4,
                          prototype5,
                          prototype6,
                          prototype7,
                          prototype8,
                          prototype9,
                          prototype10,
                          prototype11,
                          prototype12)
logitestimate
```


# Estimate Probit Model
```{r}
ProbitModel <- glm(APPROVE ~., data = mld, 
                  family = "binomial" (link = "probit"))
summary(ProbitModel)
```

## Predict probabilities for prototypical individuals
```{r}

prototype1$probitprob <- predict(ProbitModel, newdata = prototype1, type ="response")

prototype2$probitprob <- predict(ProbitModel, newdata = prototype2, type ="response")

prototype3$probitprob <- predict(ProbitModel, newdata = prototype3, type ="response")

prototype4$probitprob <- predict(ProbitModel, newdata = prototype4, type ="response")

prototype5$probitprob <- predict(ProbitModel, newdata = prototype5, type ="response")

prototype6$probitprob <- predict(ProbitModel, newdata = prototype6, type ="response")

prototype7$probitprob <- predict(ProbitModel, newdata = prototype7, type ="response")

prototype8$probitprob <- predict(ProbitModel, newdata = prototype8, type ="response")

prototype9$probitprob <- predict(ProbitModel, newdata = prototype9, type ="response")

prototype10$probitprob <- predict(ProbitModel, newdata = prototype10, type ="response")

prototype11$probitprob <- predict(ProbitModel, newdata = prototype11, type ="response")

prototype12$probitprob <- predict(ProbitModel, newdata = prototype12, type ="response")

```

```{r}
probitestimate <- rbind(prototype1,
                          prototype2,
                          prototype3,
                          prototype4,
                          prototype5,
                          prototype6,
                          prototype7,
                          prototype8,
                          prototype9,
                          prototype10,
                          prototype11,
                          prototype12)
probitestimate
```





```{r results = "asis"}
LogitOverallModel$oddratia <- exp(coef(LogitOverallModel))
variable.names(LogitOverallModel)
logittable <- as.data.frame(cbind(variable.names(LogitOverallModel),
                                  coef(LogitOverallModel),
                                  coef(summary(LogitOverallModel))[,"Std. Error"],
                                  exp(coef(LogitOverallModel))))
names(logittable) <- c("Variables", "Coefficient","SE", "Odd ratio")
kable(logittable) %>% kable_styling(full_width = FALSE)

summary(LogitOverallModel)
xtable(LogitOverallModel, type='html', html.table.attributes = "border=0") 

logLik(hispanmodel)
```


```{r}
as.data.frame(summary(ProbitModel)$coefficients)[,c("Estimate","Std. Error", "Pr(>|z|)")]

```

```{r echo = FALSE}
# mld_black <- mld %>% filter(BLACK == 1) %>%
#                     select(-BLACK,-HISPAN)
# mld_hispan <- mld %>% filter(HISPAN == 1) %>%
#                       select(-BLACK,-HISPAN)
# mld_white <- mld  %>% filter(HISPAN == 0 & BLACK == 0) %>%
#                         select(-BLACK,-HISPAN)
```



```{r results='asis'}

# # test create table for white black and hispanic logit model
# whitemodel = glm(APPROVE ~., data = mld_white, 
#                  family = "binomial" )
# wmodel_tab<- as.data.frame(summary(whitemodel)$coefficients)
# wmodel_tab$oddratio <- exp(coef(whitemodel))
# round(wmodel_tab, 4)
# 
# whitepropit <- glm(APPROVE ~., data = mld_white, 
#                  family = "binomial" (link = "probit"))
# #black model
# blackmodel = glm(APPROVE ~., data = mld_black, 
#                  family = "binomial")
# 
# bmodel_tab<- as.data.frame(summary(blackmodel)$coefficients)
# bmodel_tab$oddratio <- exp(coef(blackmodel))
# round(bmodel_tab, 4)
# 
# blackpropit <- glm(APPROVE ~., data = mld_black, 
#                  family = "binomial" (link = "probit"))
# #HIspan model
# hispanmodel = glm(APPROVE ~., data = mld_hispan, 
#                  family = "binomial")
# 
# hmodel_tab<- as.data.frame(summary(hispanmodel)$coefficients)
# hmodel_tab$oddratio <- exp(coef(hispanmodel))
# round(hmodel_tab, 4)
# 
# hispanpropit <- glm(APPROVE ~., data = mld_hispan, 
#                  family = "binomial" (link = "probit"))
# 
# 
# estimatelogit<- cbind(wmodel_tab[,c("Estimate","Std. Error", "oddratio")],
#                     bmodel_tab[,c("Estimate","Std. Error", "oddratio")],
#                     hmodel_tab[,c("Estimate","Std. Error", "oddratio")])
# 
# round(estimatelogit,4) %>%
#   kable() %>%
#   kable_styling(c("bordered"), position = "center", full_width = FALSE) %>%
#   add_header_above(c(" ", "White" = 3, "Black" = 3, "Hispan" = 3))
# 
# estimatelogit
# 
# estimateprobit <- cbind(as.data.frame(summary(whitepropit)$coefficients)[,c("Estimate","Std. Error", "Pr(>|z|)")],
#                         as.data.frame(summary(blackpropit)$coefficients)[,c("Estimate","Std. Error", "Pr(>|z|)")],
#                         as.data.frame(summary(hispanpropit)$coefficients)[,c("Estimate","Std. Error", "Pr(>|z|)")])
# 
# round(estimateprobit,4)%>%
#   kable() %>%
#   kable_styling(c("bordered"), position = "center", full_width = FALSE) %>%
#   add_header_above(c(" ", "White" = 3, "Black" = 3, "Hispan" = 3))
```



```{r}
# #White - married - guideline
# wprototype1 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT = meanOBRAT,  LOANPRC = meanLNPRC)
# #White - married - no guideline
# wprototype2 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT = meanOBRAT,  LOANPRC = meanLNPRC)
# #White - singel - guideline
# wprototype3 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT = meanOBRAT,  LOANPRC = meanLNPRC)
# #White - single - no guideline
# wprototype4 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT = meanOBRAT,  LOANPRC = meanLNPRC)
# 
# #Black - married - guideline
# bprototype5 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT= meanOBRAT,  LOANPRC = meanLNPRC)
# #Black - married - no guideline
# bprototype6 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT=meanOBRAT,  LOANPRC = meanLNPRC)
# #Black - singel - guideline
# bprototype7 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT=meanOBRAT,  LOANPRC = meanLNPRC)
# #Black - single - no guideline
# bprototype8 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT=meanOBRAT,  LOANPRC = meanLNPRC)
# 
# 
# #hispan - married - guideline
# hprototype9 <- data.frame(MARRIED = "1", GDLIN = "1", OBRAT=meanOBRAT,  LOANPRC = meanLNPRC)
# #hispan - married - no guideline
# hprototype10 <- data.frame(MARRIED = "1", GDLIN = "0", OBRAT=meanOBRAT, LOANPRC = meanLNPRC)
# #hispan - singel - guideline
# hprototype11 <- data.frame(MARRIED = "0", GDLIN = "1", OBRAT=meanOBRAT, LOANPRC = meanLNPRC)
# #hispan - single - no guideline
# hprototype12 <- data.frame(MARRIED = "0", GDLIN = "0", OBRAT=meanOBRAT,  LOANPRC = meanLNPRC)
```

```{r}
# wprototype1$logitprob <- predict(whitemodel, newdata = wprototype1, type ="response")
# 
# wprototype2$logitprob <- predict(whitemodel, newdata = wprototype2, type ="response")
# 
# wprototype3$logitprob <- predict(whitemodel, newdata = wprototype3, type ="response")
# 
# wprototype4$logitprob <- predict(whitemodel, newdata = wprototype4, type ="response")
# 
# bprototype5$logitprob <- predict(blackmodel, newdata = bprototype5, type ="response")
# 
# bprototype6$logitprob <- predict(blackmodel, newdata = bprototype6, type ="response")
# 
# bprototype7$logitprob <- predict(blackmodel, newdata = bprototype7, type ="response")
# 
# bprototype8$logitprob <- predict(blackmodel, newdata = bprototype8, type ="response")
# 
# hprototype9$logitprob <- predict(hispanmodel, newdata = hprototype9, type ="response")
# 
# hprototype10$logitprob <- predict(hispanmodel, newdata = hprototype10, type ="response")
# 
# hprototype11$logitprob <- predict(hispanmodel, newdata = hprototype11, type ="response")
# 
# hprototype12$logitprob <- predict(hispanmodel, newdata = hprototype12, type ="response")
```

```{r}
# wprototype1$probitprob <- predict(whitepropit, newdata = wprototype1, type ="response")
# 
# wprototype2$probitprob <- predict(whitepropit, newdata = wprototype2, type ="response")
# 
# wprototype3$probitprob <- predict(whitepropit, newdata = wprototype3, type ="response")
# 
# wprototype4$probitprob <- predict(whitepropit, newdata = wprototype4, type ="response")
# 
# bprototype5$probitprob <- predict(blackpropit, newdata = bprototype5, type ="response")
# 
# bprototype6$probitprob <- predict(blackpropit, newdata = bprototype6, type ="response")
# 
# bprototype7$probitprob <- predict(blackpropit, newdata = bprototype7, type ="response")
# 
# bprototype8$probitprob <- predict(blackpropit, newdata = bprototype8, type ="response")
# 
# hprototype9$probitprob <- predict(hispanpropit, newdata = hprototype9, type ="response")
# 
# hprototype10$probitprob <- predict(hispanpropit, newdata = hprototype10, type ="response")
# 
# hprototype11$probitprob <- predict(hispanpropit, newdata = hprototype11, type ="response")
# 
# hprototype12$probitprob <- predict(hispanpropit, newdata = hprototype12, type ="response")
```

```{r}
# logisepestimate <- rbind(wprototype1,
#                           wprototype2,
#                           wprototype3,
#                           wprototype4,
#                           bprototype5,
#                           bprototype6,
#                           bprototype7,
#                           bprototype8,
#                           hprototype9,
#                           hprototype10,
#                           hprototype11,
#                           hprototype12)
# logisepestimate
```



```{r}
mld %>%
      filter(APPROVE == 1, GDLIN == 0)
```

