---
title: "Paccar Parts Project Group 2"
output: html_notebook
---

```{r echo = TRUE}
# Date: 7/29/2019
# Author: Huy LE, Haodi Tu, Huibo Jia, Sourabh Gupta, Peter Broadstone
```

Clear environment of variables and packages  
=========================================

```{r message = FALSE, warning=FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```

Load packages that include different functions  
=========================================

```{r message = FALSE, warning=FALSE}
# adding library
library(tidyverse)
library(GGally)
library(gridExtra)
library("readxl")
library(janitor)
library(stringr)
library(aod)
library(ggplot2)
library(stringi)
```

Load data 
=========================================

```{r message = FALSE, warning=FALSE}
#loading data
demand <- read_csv('demand.csv')
annual_demand <- read_csv('annual_demand.csv')
# fcst_error <- read_csv('fcst_error.csv')
# future_fcst <- read_csv('future_fcst.csv')
# lead_time <- read_csv('lead_time.csv')
# item_location_count <- read_csv('item_location_count.csv')
ots <- read_csv("ots.csv")
part_info <- read_csv("part_information.csv")
protected_inventory <- read_csv("protected_inventory.csv")
```



# Adding new attributes to tables
=========================================

## Demand Table

```{r}
# Demand data & annual demand data
# change column name to vndr_id
colnames(demand)[colnames(demand)=="whse_vndr_id"] <- "vndr_id"
# cost of each rhit
demand <- demand %>% mutate(cost_rhit = 15 * rhit, 
                            year = format(order_month,"%Y"),
                            item_id = substr(dim, 1, stri_length(dim)-3))


# summary(demand)
```

## Part information table

```{r}
# part information data 
# part_info <- part_info %>% mutate_if(is.character, as.factor)

part_info <- part_info %>%  mutate(cost_inventory = round(5.5* ((length*width*height)/1728), 3)) 


# part_info <- part_info %>% mutate(item_id = substr(part_info$dim, 1, stri_length(part_info$dim)-3))

# summary(part_info)
```

## On Time Shipping table

```{r}
# On Time Shipping data
date <- as.Date.character(ots$ots_month, '%M/%D/%Y')
ots <- ots %>%  mutate(ots = (early + on_time + pd_shipped) / (past_due + total_all),
                       year = format(date,'%Y'))

# summary(ots)

```

# EDA 

```{r}
# Rfill, Rhit cost,
demand_fill <- demand %>%
                    select(year, dim, nline, rline, nhit, rhit, rhit_qty) %>%
                    group_by(year, dim) %>%
                    summarise( rfill = (1 - sum(rhit)/sum(rline)),
                               nfill = (1 - sum(nhit)/sum(nline)),
                               rhit_cost = sum(rhit)*15)
part_by_fill <- left_join(part_info, demand_fill, by = c("dim"="dim")) %>%
                  select(year, dim, marketing_category, velocity, on_hand, on_order, lead_time, vndr_id, fcst_3m, fcst_daily, safety_stock_days, safety_stock_qty, days_on_hand, part_cost, trp_ind, mx_ind, ngp_ind, lfna_ind, lfna_4c_ind, length, width, height, rfill, nfill, rhit_cost)
part_by_demand_fill <- left_join(part_by_fill, annual_demand, by = c("dim"="dim")) %>%
                  select(year, dim, marketing_category, velocity, on_hand, on_order, lead_time, vndr_id, fcst_3m, fcst_daily, safety_stock_days, safety_stock_qty, days_on_hand, part_cost, trp_ind, mx_ind, ngp_ind, lfna_ind, lfna_4c_ind, length, width, height, rfill, nfill, rhit_cost, "2014", "2015", "2016", "2017", "2018", "2019")
# filter vendors with PDC
ots = ots[ots$channel == 'PDC',]
ots$ots_month<- as.Date(ots$ots_month, format = "%m/%d/%Y")
# ots group by year and vendor
ots_by_year <- ots %>%
  mutate(year = format(ots_month,'%Y')) %>%                  
  select(year, vndr_id, early, on_time, pd_shipped, past_due, total_all) %>%
                    group_by(year, vndr_id) %>%
                    summarise( early      = sum(early),
                               on_time    = sum(on_time),
                               pd_shipped = sum(pd_shipped),
                               past_due   = sum(past_due),
                               total_all  = sum(total_all))
part_by_demand_fill <- left_join(part_by_demand_fill, ots_by_year, by = c("year"="year", "vndr_id" = "vndr_id")) %>%
                  select(year, dim, marketing_category, velocity, on_hand, on_order, lead_time, vndr_id, fcst_3m, fcst_daily, safety_stock_days, safety_stock_qty, days_on_hand, part_cost, trp_ind, mx_ind, ngp_ind, lfna_ind, lfna_4c_ind, length, width, height, rfill, nfill, rhit_cost, "2014", "2015", "2016", "2017", "2018", "2019", early, on_time, pd_shipped, past_due, total_all)
part_by_demand_fill$rfill[is.na(part_by_demand_fill$rfill)] <- 0
part_by_demand_fill$nfill[is.na(part_by_demand_fill$nfill)] <- 0
part_by_demand_fill$part_cost[is.na(part_by_demand_fill$part_cost)] <- 0
part_by_demand_fill$rhit_cost[is.na(part_by_demand_fill$rhit_cost)] <- 0
part_by_demand_fill$"2014"[is.na(part_by_demand_fill$"2014")] <- 0
part_by_demand_fill$"2015"[is.na(part_by_demand_fill$"2015")] <- 0
part_by_demand_fill$"2016"[is.na(part_by_demand_fill$"2016")] <- 0
part_by_demand_fill$"2017"[is.na(part_by_demand_fill$"2017")] <- 0
part_by_demand_fill$"2018"[is.na(part_by_demand_fill$"2018")] <- 0
part_by_demand_fill$"2019"[is.na(part_by_demand_fill$"2019")] <- 0
# write.csv(part_by_demand_fill, file = "part_by_demand_fill.csv")
```



```{r}
summary(lead_time)

summary(future_fcst)
```

# percentage of days_on_hand/lead time by vendor
```{r}

part_info %>% select(vndr_id, marketing_category, lead_time, days_on_hand, fcst_daily) %>%
            filter(fcst_daily >=1)%>%
            group_by(vndr_id) %>%
            summarise(tt_lead_time = mean(lead_time),
                      tt_daysonhand = mean(days_on_hand),
                      onhandleadrate = sum(days_on_hand)/sum(lead_time)) %>%
            mutate(turnoverstate = ifelse(tt_daysonhand <= tt_lead_time,'under','over')) %>% 
            #group_by(turnoverstate) %>%
            #summarise(count = n()) %>%
            tabyl(turnoverstate) %>%
            adorn_totals()%>%
            adorn_pct_formatting(digits = 0 )
# contribution of under 
overstockvendor <- part_info %>% select(vndr_id,dim, velocity, marketing_category, lead_time, days_on_hand, fcst_daily) %>%
            filter(fcst_daily >=1)%>%
            group_by(dim) %>% 
            summarise(tt_lead_time = mean(lead_time),
                      tt_daysonhand = mean(days_on_hand),
                      onhandleadrate = mean(days_on_hand/lead_time)) %>%
            arrange(desc(onhandleadrate))
# percentage greater than 200% overstocked vendor
overstockvendor %>% mutate(ovrstck2per = ifelse(onhandleadrate >=2, 'TRUE','FALSE')) %>%
                    tabyl(ovrstck2per) %>%
                    adorn_totals()%>%
                    adorn_pct_formatting(digits = 0 )



```

# Merging demand and part information table
============================================

```{r}
# join demand and part_info table 
new <- left_join(demand, part_info, by = c("dim", "vndr_id")) %>% filter(fcst_daily >0)

indicators <- c("mx_ind","ngp_ind","lfna_ind","lfna_4c_ind")
new[indicators] <- lapply(new[indicators], factor)
new$part_cost[is.na(new$part_cost)] <- 0

```


# Preparation for evaluating Overstocked parts

```{r}
overstocked <- new %>% 
  mutate(order_point= fcst_daily*lead_time + safety_stock_days,
         stocking_ratio = days_on_hand/ lead_time,
         factor= if_else(new$item_id %in% protected_inventory$item_id, 1,0)) %>% 
  filter(stock_class!= "N", stocking_ratio>=2, factor == 0)%>% select(-factor) 

overstocked_ind <- overstocked[which(overstocked$mx_ind == 1 |overstocked$ngp_ind == 1 |overstocked$lfna_ind == 1 |overstocked$lfna_4c_ind == 1),]

table_a_vel <- overstocked %>% group_by(item_id, velocity, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio))

table_a_mar <- overstocked %>% group_by(item_id, marketing_category, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio))


table_a_ind_vel <- overstocked_ind %>% group_by(item_id, velocity, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio))

table_a_ind_mar <- overstocked_ind %>% group_by(item_id, marketing_category, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio))

overstocked %>% group_by(item_id, marketing_category, year) %>% 
  summarise(total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_stocking_ratio = mean(stocking_ratio))


```


# Preparation for evaluating benchmark parts

```{r}
avg_stocking <- new %>% 
  mutate(order_point= fcst_daily*lead_time + safety_stock_days,
         stocking_ratio = days_on_hand/ lead_time,
         factor= if_else(new$item_id %in% protected_inventory$item_id, 1,0)) %>% 
  filter(stock_class!= "N", stocking_ratio>1 & stocking_ratio< 2, factor == 0)%>% select(-factor) 


table_b_velocity <- avg_stocking %>% group_by(velocity, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio)) 

table_b_marketing <- avg_stocking %>% group_by(marketing_category, year) %>% 
  summarise(total_rhit = sum(rhit),
            total_rline = sum(rline),
            total_rhit_qtf = sum(rhit_qty),
            avg_rfill = 1-sum(rhit)/sum(rline),
            total_rcost = sum(cost_rhit),
            total_inventory_holding_cost = sum(cost_inventory),
            total_part_cost = sum(part_cost),
            avg_lead_time = mean(lead_time),
            avg_order_point = mean(order_point),
            avg_stocking_ratio = mean(stocking_ratio)) 


```


# Calculation on saving by marketing category, velocity and year 

```{r}
# reducing avg stocking ratio by item id by
sub_table_a_vel <- table_a_vel %>% select(c(item_id, velocity, avg_stocking_ratio, year))
sub_table_a_mar <- table_a_mar %>% select(c(item_id, marketing_category, avg_stocking_ratio, year))
sub_table_a_ind_vel <- table_a_ind_vel %>% select(c(item_id, velocity, avg_stocking_ratio, year))
sub_table_a_ind_mar <- table_a_ind_mar %>% select(c(item_id, marketing_category, avg_stocking_ratio, year))
sub_table_b_velocity <- table_b_velocity %>% select(c(velocity, avg_stocking_ratio, year))
sub_table_b_marketing <- table_b_marketing %>% select(c(marketing_category, avg_stocking_ratio, year))

# difference is average desired reducing stocking ratio 
comparson_vel <- left_join(sub_table_a_vel,sub_table_b_velocity, by = c('year',"velocity")) %>% mutate(difference = avg_stocking_ratio.x - avg_stocking_ratio.y)
comparson_mar <- left_join(sub_table_a_mar,sub_table_b_marketing, by = c('year',"marketing_category")) %>% mutate(difference = avg_stocking_ratio.x - avg_stocking_ratio.y)
comparson_ind_vel <- left_join(sub_table_a_ind_vel,sub_table_b_velocity, by = c('year',"velocity")) %>% mutate(difference = avg_stocking_ratio.x - avg_stocking_ratio.y)
comparson_ind_mar <- left_join(sub_table_a_ind_mar,sub_table_b_marketing, by = c('year',"marketing_category")) %>% mutate(difference = avg_stocking_ratio.x - avg_stocking_ratio.y)
# On hand qty = stocking ratio* lead time * daily fcst 

df_vel <- left_join(comparson_vel, new, by = c("item_id", 'velocity', 'year'))
df_mar <- left_join(comparson_mar, new, by = c("item_id", 'marketing_category', 'year'))
df_ind_vel <- left_join(comparson_ind_vel, new, by = c("item_id", 'velocity', 'year'))
df_ind_mar <- left_join(comparson_ind_mar, new, by = c("item_id", 'marketing_category', 'year'))

final_vel <- df_vel %>% group_by(item_id,velocity,year) %>% 
  summarise(reduce_on_hand = round(mean(difference)*mean(lead_time)*mean(fcst_daily), 0),
            saving_part_cost = sum(part_cost)*reduce_on_hand,
            saving_holding_costing = sum(cost_inventory)*reduce_on_hand)

final_mar <- df_mar %>% group_by(item_id,marketing_category, year) %>% 
  summarise(reduce_on_hand = round(mean(difference)*mean(lead_time)*mean(fcst_daily), 0),
            saving_part_cost = sum(part_cost)*reduce_on_hand,
            saving_holding_costing = sum(cost_inventory)*reduce_on_hand)

final_ind_vel <- df_ind_vel %>% group_by(item_id,velocity, year) %>% 
  summarise(reduce_on_hand = round(mean(difference)*mean(lead_time)*mean(fcst_daily), 0),
            saving_part_cost = sum(part_cost)*reduce_on_hand,
            saving_holding_costing = sum(cost_inventory)*reduce_on_hand)

final_ind_mar <- df_ind_mar %>% group_by(item_id,marketing_category, year) %>% 
  summarise(reduce_on_hand = round(mean(difference)*mean(lead_time)*mean(fcst_daily), 0),
            saving_part_cost = sum(part_cost)*reduce_on_hand,
            saving_holding_costing = sum(cost_inventory)*reduce_on_hand)
 


# write.csv(final_vel, 'final_vel.csv',row.names=FALSE)
# write.csv(final_mar, 'final_mar.csv',row.names=FALSE)
# write.csv(final_ind_vel, 'final_ind_vel.csv', row.names=FALSE)
# write.csv(final_ind_mar, 'final_ind_mar.csv', row.names=FALSE)
```





# Preparation for evaluating understocked parts


```{r}
new$stocking_ratio = new$days_on_hand / new$lead_time

new <- subset(new, whse_stk_ind != "N")

understocked <- subset(new, stocking_ratio < 1)

understocked$stocking_ratio_increase <- 1 - understocked$stocking_ratio

understocked$cost_increase <- understocked$cost_inventory * understocked$stocking_ratio_increase * understocked$fcst_daily
```



# Calculation on understocked parts

## What will be the total cost of increasing the on hand stock to 1 (per year)
```{r}
sum(understocked$cost_increase) / 2.5
```

## How much extra space is needed if we increase?
```{r}
sum(understocked$cost_increase) / 5.5 / 2.5

sum(understocked$rhit) / sum(understocked$rline)
```


## Which stocking_ratio has the best rhit ratio?
```{r}
new <- mutate(new, stock_ratio_group =
ifelse(stocking_ratio < 1, "Understocked",
ifelse(1 <= stocking_ratio & stocking_ratio <= 2, "Good",
ifelse(2 < stocking_ratio, "Overstocked", "Error"))))


new %>%
  group_by(stock_ratio_group) %>%
  summarise(sum_rline = sum(rline),
            sum_rhits = sum(rhit),
            ratio_of_hits = sum_rhits / sum_rline,
            regional_fill_rate = (1 - ratio_of_hits) * 100)
```

+ Understocked has a regional fill rate of 95.9% and good has a regional fill rate of 97.2%


## How many rhits are there per year for the understocked items?
```{r}
sum(understocked$rhit) / 2.5
```


## What is the cost of the rhits per year?
```{r}
sum(understocked$rhit) * 15 / 2.5
```

+ This is the overall cost of rhits if we don't change stocking levels


## What is the projected savings on rhits if we change the levels?
```{r}
285792 * (0.04064424 - 0.02806076) * 15 / 2.5
```



## Completing the above for individual velocity
```{r}
new %>%
  group_by(velocity, stock_ratio_group) %>%
  summarise(sum_rline = sum(rline),
            sum_rhits = sum(rhit),
            ratio_of_hits = sum_rhits / sum_rline,
            regional_fill_rate = (1 - ratio_of_hits) * 100)
```


## Repeat the calculations for items with ind_sum = 1
```{r}
understocked$mx_ind <- as.integer(as.character(understocked$mx_ind))
summary(understocked$mx_ind)
```


```{r}
understocked$ngp_ind <- as.integer(as.character(understocked$ngp_ind))
summary(understocked$ngp_ind)
```


```{r}
understocked$lfna_ind <- as.integer(as.character(understocked$lfna_ind))
summary(understocked$lfna_ind)
```


```{r}
understocked$trp_ind <- as.integer(as.character(understocked$trp_ind))
summary(understocked$trp_ind)
```


```{r}
understocked$ind_sum <- understocked$trp_ind + understocked$mx_ind + understocked$ngp_ind + understocked$lfna_ind

understocked <- mutate(understocked, ind_sum = ifelse(ind_sum > 0, 1, 0))

summary(understocked$ind_sum)
```


+ Also a 1.3% increase 97.5% - 96.2%


### Splitting for parts that PACCAR wants a 100% rfill rate
```{r}
fill100 <- subset(understocked, ind_sum == 1)
```


## How many rhits are there per year for the fill100 items?
```{r}
sum(fill100$rhit) / 2.5
```


## What is the cost of the rhits per year?
```{r}
sum(fill100$rhit) * 15 / 2.5
```


## What is the projected savings on rhits if we change the levels?
```{r}
73440 * (0.03747084 - 0.02479471) * 15 / 2.5
```


## What will be the total cost of increasing the on hand stock to 1 (per year)
```{r}
sum(fill100$cost_increase) / 2.5
```


## How much extra space is needed if we increase?
```{r}
sum(fill100$cost_increase) / 5.5 / 2.5
```



# Testing with neural network model (Failed)

```{r}
# library(neuralnet)
# library(MASS)
# library(caret)
# colnames(fdataset)
# #c("velocity","lead_time","safety_stock_qty","part_cost","trp_ind","mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","whse_stk_ind" )
# #fdataset[,c("mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","demand_qty","lead_time","safety_stock_qty","part_cost")]
# fdataset$velocity <- ifelse(fdataset$velocity %in% c(1,2,3,9),fdataset$velocity,10)
# fdataset$whse_stk_ind <-  ifelse(fdataset$whse_stk_ind == 'N',0,1)
# maxval <-apply(fdataset[,c("lead_time","safety_stock_qty","part_cost","trp_ind","mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","whse_stk_ind" )],2,max)
# minval <-apply(fdataset[,c("lead_time","safety_stock_qty","part_cost","trp_ind","mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","whse_stk_ind" )],2,min)
# fdatasetN <- fdataset
# fdatasetN$trp_ind <- as.numeric(fdatasetN$trp_ind)
# fdatasetN$mx_ind <- as.numeric(fdatasetN$mx_ind ) 
# fdatasetN$ngp_ind <- as.numeric(fdatasetN$ngp_ind ) 
# fdatasetN$lfna_ind <- as.numeric(fdatasetN$lfna_ind ) 
# fdatasetN$lfna_4c_ind <- as.numeric(fdatasetN$lfna_4c_ind ) 
# fdatasetN$whse_stk_ind <- as.numeric(fdatasetN$whse_stk_ind ) 
# str(fdatasetN)
# fdatasetN[,c("lead_time","safety_stock_qty","part_cost","trp_ind","mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","whse_stk_ind" )] <- as.data.frame(scale(fdatasetN[,c("lead_time","safety_stock_qty","part_cost","trp_ind","mx_ind","ngp_ind","lfna_ind","lfna_4c_ind","whse_stk_ind" )], center = minval, scale = (as.numeric(maxval)-as.numeric(minval))))
# trainsetN <- fdatasetN %>% filter(order_month  <'2018-01-01')
# testsetN<- fdatasetN %>% filter(order_month  >='2019-01-01')
# index <- sample(1:nrow(trainsetN), size =5000)
# strainsetN <- trainsetN[index,]
# strainsetN
# #A model with 4 nodes on the hidden 
# layernm1 <- neuralnet(demand_qty~lead_time+safety_stock_qty+part_cost+trp_ind, hidden = c(2), data=strainsetN,stepmax=1e6)
# plot(layernm1)
```



