---
title: "AWS cost management"
author: "Sourabh Gupta, Peter Broadstone, Huibo, Huy Le, Haodi Tu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

```{r}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


```{r}
# adding library to be used in code
library(tidyverse)
library(GGally)
library(gridExtra)
library("readxl")
library(janitor)
library(stringr)
library(aod)
library(ggplot2)
library(stringi)
library(reshape2)

# reading the dataset exported from data manipulation code
full_dta <- read_csv('full_dta.csv')
```


# Optional for splitting data into training and test sets
```{r}
# Training and validation sets
# training is from month "04" and "05"
# validation is from month "06"
training <- subset(full_dta, full_dta$month == "04" | full_dta$month == "05")
validation <- subset(full_dta, full_dta$month == "06")

# indexing, sampling and removing records where month is null
index <- sample(1:nrow(training), 3000, replace = TRUE)
training <- training[index,]
training <- training[!is.na(training$month), ]

# mutate Binary variables from "yes" "no" to 1 and 0 respectively
training$Visualize <- ifelse(training$Visualize == "Yes", 1,0)
training$Alert <- ifelse(training$Alert == "Yes", 1,0)
training$Report <- ifelse(training$Report == "Yes", 1,0)

# summary of the final training dataset
summary(training)
```


# Variable by month
## What are the counts, Billed_amounts, money per by Customer_size?
```{r}
# 1st visual - Group customers by size and visualize total billing amount and average bill per customer
# creating required dataframe for this visual
Customer_size_group <- full_dta %>%
  group_by(Customer_size, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 1st visual - Group customers by size and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph 
ggplot(data = Customer_size_group, aes(x = Month, y = total_billed_amt, fill = Customer_size)) +
  geom_bar(stat = "identity", position = "dodge")
```


## What are the counts, Billed_amounts, money per by Geo_Code?
```{r}
# 2nd visual - Group customers by geo_code (graphical location) and visualize total billing amount and average bill per customer
# creating required dataframe for this visual 
Geo_Code_group <- full_dta %>%
  group_by(Geo_Code, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 2nd visual - Group customers by geo_code (graphical location) and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Geo_Code_group, aes(x = Month, y = total_billed_amt, fill = Geo_Code)) +
  geom_bar(stat = "identity", position = "dodge")
```


## What are the counts, Billed_amounts, money per by Visualize?
```{r}
# 3rd visual - Group customers by usage of Visualize tool and visualize total billing amount and average bill per customer
# creating required dataframe for this visual 
Visualize_group <- full_dta %>%
  group_by(Visualize, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 3rd visual - Group customers by usage of Visualize tool and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Visualize_group, aes(x = Month, y = total_billed_amt, fill = Visualize)) +
  geom_bar(stat = "identity", position = "dodge")
```


## What are the counts, Billed_amounts, money per by Alert?
```{r}
# 4th visual - Group customers by usage of Alert tool and visualize total billing amount and average bill per customer
# creating required dataframe for this visual 
Alert_group <- full_dta %>%
  group_by(Alert, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 4th visual - Group customers by usage of Alert tool and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Alert_group, aes(x = Month, y = total_billed_amt, fill = Alert)) +
  geom_bar(stat = "identity", position = "dodge")
```


## What are the counts, Billed_amounts, money per by Report?
```{r}
# 5th visual - Group customers by usage of Report tool and visualize total billing amount and average bill per customer
# creating required dataframe for this visual
Report_group <- full_dta %>%
  group_by(Report, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 5th visual - Group customers by usage of Report tool and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Report_group, aes(x = Month, y = total_billed_amt, fill = Report)) +
  geom_bar(stat = "identity", position = "dodge")
```


## What are the counts, Billed_amounts, money per by age_year?
```{r}
# 6th visual - Group customers by age of customer (categorical variable in final_dta dataset, created in data manipulation file) and visualize total billing amount and average bill per customer
# creating required dataframe for this visual
age_year_group <- full_dta %>%
  group_by(age_year, Month) %>%
  summarise(count = n(),
            total_billed_amt = sum(Billed_amount),
            billed_per_cust = total_billed_amt / count) %>%
  arrange(-total_billed_amt)
```


```{r}
# 6th visual - Group customers by age of customer (categorical variable in final_dta dataset, created in data manipulation file) and visualize total billing amount and average bill per customer
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = age_year_group, aes(x = Month, y = total_billed_amt, fill = age_year)) +
  geom_bar(stat = "identity", position = "dodge")
```


# Variables with Visualize, Alert, and Report percentages
## Usage Percentages by Customer_size
```{r}
# 7th visual - Group customers by Customer size and visualize total usage of our 3 products
# creating required dataframe for this visual
Pct_by_Customer_size <- full_dta %>%
  group_by(Customer_size) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            viz_pct = (viz_yes / count) * 100,
            alert_yes = sum(Alert == "Yes"),
            alert_pct = (alert_yes / count) * 100,
            report_yes = sum(Report == "Yes"),
            report_pct = (report_yes / count) * 100)
```


```{r}
# 7th visual - Group customers by Customer size and visualize total usage of our 3 products
Pct_by_Customer_size_melt <- melt(Pct_by_Customer_size, id = "Customer_size", measure = c("viz_pct", "alert_pct", "report_pct"))
```


```{r}
# 7th visual - Group customers by Customer size and visualize total usage of our 3 products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Pct_by_Customer_size_melt, aes(x = Customer_size, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ As the companies get larger, the usage percentages increase


## Usage Percentages by Geo_Code
```{r}
# 8th visual - Group customers by Geographical Location of customer and visualize total usage of our 3 products
# creating required dataframe for this visual
Pct_by_Geo_Code <- full_dta %>%
  group_by(Geo_Code) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            viz_pct = viz_yes / count,
            alert_yes = sum(Alert == "Yes"),
            alert_pct = alert_yes / count,
            report_yes = sum(Report == "Yes"),
            report_pct = report_yes / count)
```


```{r}
# 8th visual - Group customers by Geographical Location of customer and visualize total usage of our 3 products
Pct_by_Geo_Code_melt <- melt(Pct_by_Geo_Code, id = "Geo_Code", measure = c("viz_pct", "alert_pct", "report_pct"))
```


```{r}
# 8th visual - Group customers by Geographical Location of customer and visualize total usage of our 3 products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Pct_by_Geo_Code_melt, aes(x = Geo_Code, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ EMEA are the highest users of Visualize followed by APAC, AMER, and JAPN
+ GLBL is the highest user of Alert and Report
+ CHNA are the lowest users of all three


## Usage Percentages by age_year
```{r}
# 9th visual - Group customers by Customer age and visualize total usage of our 3 products
# creating required dataframe for this visual
Pct_by_age_year <- full_dta %>%
  group_by(age_year) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            viz_pct = viz_yes / count,
            alert_yes = sum(Alert == "Yes"),
            alert_pct = alert_yes / count,
            report_yes = sum(Report == "Yes"),
            report_pct = report_yes / count)
```


```{r}
# 9th visual - Group customers by Customer age and visualize total usage of our 3 products
Pct_by_age_year_melt <- melt(Pct_by_age_year, id = "age_year", measure = c("viz_pct", "alert_pct", "report_pct"))
```


```{r}
# 9th visual - Group customers by Customer age and visualize total usage of our 3 products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = Pct_by_age_year_melt, aes(x = age_year, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ Members for less than a year tend to use Visualize and Report less than other groups
+ Members for 1-3 years are the highest users of Alert
+ In general, Report usage increases as a customer is a member for longer


## Visualize by Alert and Report
```{r}
# 10th visual - Group customers by Customer age and visualize total usage of our visualize by Alert and report products
# creating required dataframe for this visual
viz_by_alert_report <- full_dta %>%
  group_by(Visualize) %>%
  summarise(count = n(),
            alert_yes = sum(Alert == "Yes"),
            alert_pct = alert_yes / count,
            report_yes = sum(Report == "Yes"),
            report_pct = report_yes / count)
```


```{r}
# 10th visual - Group customers by Customer age and visualize total usage of our visualize by Alert and report products
# creating required dataframe for this visual
viz_by_alert_report_melt <- melt(viz_by_alert_report, id = "Visualize", measure = c("alert_pct", "report_pct"))
```


```{r}
# 10th visual - Group customers by Customer age and visualize total usage of our visualize by Alert and report products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = viz_by_alert_report_melt, aes(x = Visualize, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ Customers who use Visualize are more likely to use Alert and Report


## Alert by Visualize and Report
```{r}
# 11th visual - Group customers by Customer age and visualize total usage of our Alert by visualize and report products
# creating required dataframe for this visual
alert_by_viz_report <- full_dta %>%
  group_by(Alert) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            viz_pct = viz_yes / count,
            report_yes = sum(Report == "Yes"),
            report_pct = report_yes / count)
```


```{r}
# 11th visual - Group customers by Customer age and visualize total usage of our Alert by visualize and report products
# creating required dataframe for this visual
alert_by_viz_report_melt <- melt(alert_by_viz_report, id = "Alert", measure = c("viz_pct", "report_pct"))
```


```{r}
# 11th visual - Group customers by Customer age and visualize total usage of our Alert by visualize and report products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = alert_by_viz_report_melt, aes(x = Alert, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ Customers who use Alert are more likely to use Visualize and Report


## Report by Visualize and Report
```{r}
# 12th visual - Group customers by Customer age and visualize total usage of our Report by visualize and Alert products
# creating required dataframe for this visual
report_by_viz_alert <- full_dta %>%
  group_by(Report) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            viz_pct = viz_yes / count,
            alert_yes = sum(Alert == "Yes"),
            alert_pct = alert_yes / count)
```


```{r}
# 12th visual - Group customers by Customer age and visualize total usage of our Report by visualize and Alert products
# creating required dataframe for this visual
report_by_viz_alert_melt <- melt(report_by_viz_alert, id = "Report", measure = c("viz_pct", "alert_pct"))
```


```{r}
# 12th visual - Group customers by Customer age and visualize total usage of our Report by visualize and Alert products
# Using GGplot, creating bar graph, no aggregating of data here
ggplot(data = report_by_viz_alert_melt, aes(x = Report, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge")
```

+ Customers who use Report are more likely to use Visualize and Alert


# What percentage of customers fit into each category of Visualize, Alert, Report
```{r}
# 13th visual - Group customers by %age of Customer and visualize total usage of our all 3 products
# creating required dataframe for this visual
viz_alert_report_pct <- full_dta %>%
  group_by(Visualize, Alert, Report) %>%
  summarise(count = n(),
            pct_of_customer = (count / 1634886) * 100)
```

+ Can make this into a graph if we want to use it

+ If a customer uses either visualize, alert, or report, they are __% more likely to use another of the three


# Looking at trends by month
## First group by Customer_ID and month
```{r}
# 14th visual - Trend of billing of our customer in last 3 months based on all categorical variables we have
# creating required dataframe for this visual
cust_id_groups <- full_dta %>%
  group_by(Customer_ID, Month, Customer_size, Geo_Code, Visualize, Alert, Report, age_year) %>%
  summarise(count_products = n(),
            total_billed = sum(Billed_amount))
```


```{r}
# 15th visual - Trend of percentage usage of our products by our customer in last 3 months based on month
# creating required dataframe for this visual
cust_id_groups %>%
  group_by(Month) %>%
  summarise(total_customers = n(),
            total_billed_amt = sum(total_billed),
            viz_pct = (sum(Visualize == "Yes") / total_customers) * 100,
            alert_pct = (sum(Alert == "Yes") / total_customers) * 100,
            report_pct = (sum(Report == "Yes") / total_customers) * 100)
```


# Product Matrix
## Use all three products
```{r}
# Product matrix usage for all 3 products
sum(cust_id_groups$Visualize == "Yes" & cust_id_groups$Alert == "Yes" & cust_id_groups$Report == "Yes")
```

+ 0.5% use all three products


## Use two of three products
```{r}
# use of 2 products based on 3rd - part 1
sum(cust_id_groups$Visualize == "Yes" & cust_id_groups$Alert == "Yes" & cust_id_groups$Report == "No")
sum(cust_id_groups$Visualize == "Yes" & cust_id_groups$Alert == "No" & cust_id_groups$Report == "Yes")
sum(cust_id_groups$Visualize == "No" & cust_id_groups$Alert == "Yes" & cust_id_groups$Report == "Yes")
```

+ Total is 6878
+ 4.9% use two of three products


## Use one of three products
```{r}
# use of 2 products based on 3rd - part 2
sum(cust_id_groups$Visualize == "Yes" & cust_id_groups$Alert == "No" & cust_id_groups$Report == "No")
sum(cust_id_groups$Visualize == "No" & cust_id_groups$Alert == "Yes" & cust_id_groups$Report == "No")
sum(cust_id_groups$Visualize == "No" & cust_id_groups$Alert == "No" & cust_id_groups$Report == "Yes")
```

+ 36962
+ 26.4% use one of three products

## Use none of three products
```{r}
# usage of none of our products
sum(cust_id_groups$Visualize == "No" & cust_id_groups$Alert == "No" & cust_id_groups$Report == "No")
```

+ 68.2% use none of three products


# Looking at anomalies in billing data
```{r}
# anomalies in the billing data, specially negative values
summary(cust_id_groups$total_billed)
```


```{r}
# total customers with total billing amount = 0 based on customer groups
sum(cust_id_groups$total_billed == 0)
free_month <- subset(cust_id_groups, total_billed == 0)
```


```{r}
# total of records where billing is less than or equal to 0
sum(full_dta$Billed_amount <= 0)
```


```{r}
# customers where billing is too high, may be a typo or error or continous running clustures 
sum(cust_id_groups$total_billed > 275000)
high_billing <- subset(cust_id_groups, total_billed > 275000)
```


```{r}
# draw graphs for customer billing amount less than 100000
cust_id_groups %>%
  filter(total_billed < 100000) %>%
  ggplot(aes(x = total_billed)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
```


# Product Usage by Customer Size for Presentation
```{r}
# FInal graph -1 : percentage of customers using different bill management tools
Pct_by_Customer_size <- full_dta %>%
  group_by(Customer_size) %>%
  summarise(count = n(),
            viz_yes = sum(Visualize == "Yes"),
            Visualize = (viz_yes / count) * 100,
            alert_yes = sum(Alert == "Yes"),
            Alert = (alert_yes / count) * 100,
            report_yes = sum(Report == "Yes"),
            Report = (report_yes / count) * 100)
```


```{r}
Pct_by_Customer_size_melt <- melt(Pct_by_Customer_size, id = "Customer_size", measure = c("Visualize", "Alert", "Report"))
```


```{r}
# FInal graph -2 : percentage of customers using different bill management tools
ggplot(data = Pct_by_Customer_size_melt, aes(x = Customer_size, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge", colour = "black") +
  theme_classic() +
  labs(fill = "Product") +
  xlab("Customer Size") +
  ylab("Product Usage Percentage") +
  theme(axis.text = element_text(face = "bold", size = 9),
        axis.ticks.x = element_blank(),
        legend.position = "top",
        legend.title = element_text(face = "bold")) +
  scale_fill_brewer(palette = "Blues") +
  geom_text(aes(label = round(value, 1)), vjust = -0.5, color = "black",
            position = position_dodge(.9), size = 3.5)
```






















